First steps towards a formalization of Forcing

### 2018-11-19 LSFA/related.tex
spell check

\subsection{Related work}\label{sec:related-work}
Formalization of mathematics serves many purposes
\cite{simpson-theorem-proving-math}. The most obvious one is to
increase reliability in a result and/or its proof. This has been the
original motivation that lead Voevodsky to gather many researchers
around \emph{homotopy type theory} and its formalization in Coq
\cite{hottbook}; the same applies to the four colour theorem (checked
by Gonthier \cite{MR2463991}) and the formidable \emph{Flyspeck}
project \cite{MR3659768} by the team conducted by Hales.

@@

There is another major framework in Isabelle based on higher order
logic, Isabelle/HOL. This framework is very active, and as a 
consequence more automated tools are available. Isabelle/HOL has 
basic chapters on set theory. One of those, by Steven Obua, proceeds up to
well founded relations and provides translations between types in HOL
(for instance \isatt{nat}) to  sets  (elements of type
\isatt{ZF}). Another one, by A.~Popescu and D.~Traytel, reaches
cardinal artihmetic. This is fairly limited for our purposes.

>>>>

\subsection{Related work}\label{sec:related-work}
Formalization of mathematics serves many purposes
\cite{simpson-theorem-proving-math}. The most obvious one is to
increase reliability in a result and/or its proof. This has been the
original motivation that lead Voevodsky to gather many researchers
around \emph{homotopy type theory} and its formalization in Coq
\cite{hottbook}; the same applies to the four color theorem (checked
by Gonthier \cite{MR2463991}) and the formidable \emph{Flyspeck}
project \cite{MR3659768} by the team conducted by Hales.

@@

There is another major framework in Isabelle based on higher order
logic, Isabelle/HOL. This framework is very active, and as a 
consequence more automated tools are available. Isabelle/HOL has 
basic chapters on set theory. One of those, by Steven Obua, proceeds up to
well founded relations and provides translations between types in HOL
(for instance \isatt{nat}) to  sets  (elements of type
\isatt{ZF}). Another one, by A.~Popescu and D.~Traytel, reaches
cardinal arithmetic. This is fairly limited for our purposes.
